Global phase diagram and possible quantum spin liquid in the triangular $J$-$K$-$\Gamma$ model

### 2020-08-01 paper/paper.tex
20200801 20:05

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \includegraphics[width=\linewidth]{fig/SecondDerivatives.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) (a) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, four different stripe phases designated as Stripe-A, Stripe-B, Stripe-C and Stripe-D, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase. The three FM phases different from each other in the direction of the ordered moment, and also the four stripe phases are distinguished by their moment directions, see main text for details. (b) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=1.5\pi$. (c) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=0$. (d) The red (blue) line is $-\partial^2E_0/\partial\beta^2$ ($E_0$) versus $\beta$ with $\alpha=0.3\pi$.}
\end{figure*}

@@

@@

\section{\label{apx:AppendixA}Classical ground states for some special model parameters}

@@

\section{\label{apx:AppendixB}Classical energy and moment direction of the stripe ordered states}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) (a) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, four different stripe phases designated as Stripe-A, Stripe-B, Stripe-C and Stripe-D, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase. The three FM phases different from each other in the direction of the ordered moment, and also the four stripe phases are distinguished by their moment directions, see main text for details. (b) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=1.5\pi$. (c) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=0$. (d) The red (blue) line is $-\partial^2E_0/\partial\beta^2$ ($E_0$) versus $\beta$ with $\alpha=0.3\pi$.}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/SixSitesOrder.pdf}
    \caption{\label{fig:SixSitesOrder}(Color online) Spin configuration and spin structure factor for \emph{six-chains stripe order}. The green dashed line in (b) marks the first Brillouin Zone.}
\end{figure}

@@

\section{\label{apx:AppendixA}Phase Boundaries in the Quantum Phase Diagram}

To obtain the quantum phase diagram of the model \eqref{eq:Hamiltonian}, we perform exact-diagnoalization calculations of the GS of the Hamiltonian\eqref{eq:Hamiltonian} on a $4 \times 6$ cluster with the periodic boundary conditions. The phase boundaries are obtained from the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$. Some representive curves are shown in Fig.~\ref{fig:SecondDerivatives}. For Fig.~\ref{fig:SecondDerivatives}(a), $\alpha=0.05\pi$, the second derivative of $E_0$ versus $\beta$ has two peaks located at $\beta=-0.01\pi$ and $\beta=0.81\pi$, which are the phase boundaries between the FM-A and QSL phase. As we increase $\alpha$ to $0.3\pi$, there are three singularities in the second derivatives, see Fig.~\ref{fig:SecondDerivatives}(b). The small peak at $\beta=0.62\pi$ indicates the phase transition from Stripe-C to Stripe-B and the other two sharp peaks at $\beta=0.94\pi$ and $\beta=1.87\pi$ originate from the phase transitions from Stripe-B to FM-A and from FM-A to Stripe-C. Fig~\ref{fig:SecondDerivatives}(c) show the case for $\alpha=0.75\pi$, the two peaks located at $\beta=0.87\pi$ and $\beta=1.89\pi$ signifying the phase transitions between Stripe-B and FM-C. On the other hand, we can also fix $\beta$ to detect the phase transitions with varying $\alpha$'s and the corresponding results are shown in Fig.~\ref{fig:SecondDerivatives}(d)-(f). In Fig.~\ref{fig:SecondDerivatives}(d), $\beta$ equals to $0$, the first two sharp peaks at $\alpha=0.045\pi$and $\alpha=0.097\pi$ reveal the phase transitions from FM-A to QSL and further to Stripe-C. The broad peak at about $\alpha=0.5\pi$ is due to the phase transitions from Stripe-C to Stripe-D to Stripe-B. The last singularity at $\alpha=0.93\pi$ marks the phase boundary between Stripe-B and FM-C. In Fig.~\ref{fig:SecondDerivatives}(e) we show the phase transition between \emph{modulated six chains stripe} and 120$^\circ$ N\'{e}el as well as the phase transition from 120$^\circ$ N\'{e}el to Stripe-B. $\beta$ is fixed to $0.5\pi$ and transitions occur at $\alpha=0.32\pi$ and $\alpha=0.62\pi$ respectively. Last but not least, we show there are phase transitions between these different FM phases. See Fig.~\ref{fig:SecondDerivatives}(f) where $\beta=1.5\pi$, the sharp peak at $\alpha=0.5\pi$ shows that the FM-A phase for the HK model is a cirtical point, infinitesimal $\Gamma$ interaction will cause phase transition to other FM phases which have different moment direction from FM-A phase.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/SecondDerivatives.pdf}
    \caption{\label{fig:SecondDerivatives}Second derivatives of ground state energies versus $\alpha$ or $\beta$. The blue lines are the ground state energies and the red lines are the second derivatives. (a)-(c) $-\partial^2E_0/\partial\beta^2$ with $\alpha$ fixed to $0.05\pi$, $0.3\pi$ and $0.75\pi$, respectively. (d)-(f) $-\partial^2E_0/\partial\alpha^2$ with $\beta$ fixed to $0$, $0.5\pi$ and $1.5\pi$, respectively.}
\end{figure}

\section{\label{apx:AppendixB}Quantum Static Spin Structure Factors}

Here we provide additional spin structure factor profiles as a supplement to these profiles shown in the main text. For classical 120$^\circ$ N\'{e}el state, the SSF has high intensity at the corner of the first BZ, i.e., $\tilde{K}$ points and the SSF peaked at the middle points of $\tilde{\Gamma}$ and $\tilde{K}$'s for classical Dual N\'{e}el state. Fig.~\ref{fig:AppendixSSF}(a) and (b) show the SSF profiles calculated from our exact diagnoalization ground state at $\alpha=0.5\pi, \beta=0.5\pi$ and $\alpha=0.5\pi, \beta=1.85\pi$ which belong the 120$^\circ$ N\'{e}el phase and Dual N\'{e}el phase respectively. For both profile, though the SSF intensity is diffusive in the reciprocal space, the points with highest intensity are consistent with the classical states.

In the main text, we show the SSF profiles for $alpha=0$ and $\alpha=\pi$, which provide evidence that the ground state for the pure $\Gamma$ model is FM ordered. However, these two points are too close to the phase boundary. One might question whether the SSF profiles of these two points are typical for the whole region. Here we show another two SSF profiles with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ which belong to FM-A phase and FM-C phase respectively. Both SSF profile has high intensity at $\tilde{\Gamma}$ point, which is a typical characteristic of FM ordered state.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/AppendixSSF.pdf}
    \caption{\label{fig:AppendixSSF}(Color online) Static spin structure factors for some representative model parameters.}
\end{figure}

\section{\label{apx:AppendixC}Classical ground states for some special model parameters}

@@

\section{\label{apx:AppendixD}Classical energy and moment direction of the stripe ordered states}
